Revision Memo for, ``Government Websites As Data: A methodological pipeline with application to the websites of municipalities in the United States''

### 2021-06-04 paper/jitp_rr_memo/jitp_rr_memo.tex
made a change to the reviewer memo to reflect the literature section being split in two

    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection at the end of the literature section address this point. See also our responses to R2's comments 1--3.

>>>>

    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection in Section 2 (with the former contents of Section 2 being moved down to Section 3) address this point. See also our responses to R2's comments 1--3.
